---
title: "Extra Credit Assignment02_Data607"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
```

```{r }
movie_rating<-read_excel("F:\\CUNY masters\\extra credit assignment 607\\607 2nd extra credit\\movie_rating.xlsx",sheet=1,range="A1:G6",
              col_name=TRUE,col_types=NULL)
movie_rating 
```
```{r }
movie_rating1<-movie_rating[c("Barbarian","Funnypage","Holdmetight","Nope","Prey","Theterritory")]
movie_rating1
movie_rating1<-movie_rating1 %>% mutate(user_avg=rowMeans(movie_rating1,na.rm=TRUE,dims=1))
movie_rating1
```
```{r}
movie_avg<-colMeans(movie_rating[sapply(movie_rating, is.numeric)],na.rm=TRUE)
movie_avg
mean_movie<-mean(movie_avg)
mean_movie
movie_avg_minus_mean_movie<-movie_avg-mean_movie
movie_avg_minus_mean_movie
user_avg_minus_mean_movie<-movie_rating1$user_avg-mean_movie
user_avg_minus_mean_movie
```
```{r}
movie<-c("Barbarian","Funnypage","Holdmetight","Nope","Prey","Theterritory")
user_avg<-movie_rating1$user_avg
movie_avg

df_new <- cbind(movie_rating,user_avg,user_avg_minus_mean_movie)
df_new
```
```{r}
df1<-data.frame(movie_avg,movie_avg_minus_mean_movie)
df1
```
## Finding rate by Global Baseline Estimate
**Question1: How would Monir rate Theterritory?
** Question2: How would Karim rate Prey?
**Question3: How would Joseph rate Prey and Theterritory?
** Question4: How would Prakash rate Prey?

**General Formula: Global Baseline Estimate = Mean Movie Rating + movie rating relative to average + Critic's rating relative to average.

```{r}
Monir_rating_for_Theterritory<-2.905556 -1.5722222+0.09444444
Monir_rating_for_Theterritory
Karim_rating_for_Prey<-2.905556 -0.4055556+0.09444444
Karim_rating_for_Prey
Joseph_rating_for_Prey<-2.905556 -0.4055556+0.59444444
Joseph_rating_for_Prey
Joseph_rating_for_Theterritory<-2.905556-1.5722222+0.59444444
Joseph_rating_for_Theterritory
Prakash_rating_for_Prey<-2.905556-0.4055556+0.09444444
Prakash_rating_for_Prey
```
#Above 4 questions answers are presented below in tabular form
```{r}
unseen_movie_rating<-data.frame(Monir_rating_for_Theterritory,Karim_rating_for_Prey,Joseph_rating_for_Prey,Joseph_rating_for_Theterritory,Prakash_rating_for_Prey)
unseen_movie_rating
```
**Recommending Prey for Karim


